Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-18 paper.tex
No dot in keywords
fix axis label

  \keywords{Forward Reasoning \and Forward Chaining \and Tactics \and Interactive Theorem Proving.}
\end{abstract}

@@

\begin{figure}
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        title={Depth Test},
        xlabel={Depth},
        ylabel={Time in ms},
        xmin=1, xmax=5,
        ymin=8, ymax=2^10,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 35.466292) (2, 40.918638) (3, 46.936125) (4, 54.933124) (5, 61.269861)
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 135.967736) (2, 127.324444) (3, 136.891250) (4, 118.720444) (5, 116.293222) 
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          ]
          coordinates {
            (1, 107.978069) (2, 115.900527) (3, 122.454958) (4, 137.732764) (5, 144.037681) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 619.932611) (2, 601.456805) (3, 600.926110) (4, 589.144389) (5, 595.091180) 
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Depth benchmark no-precompilation}%
    \label{fig:erase-noprecomp}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        title={Depth Test},
        xlabel={Depth},
        %ylabel={Time in ms},
        xmin=1, xmax=5,
        ymin=8, ymax=1024,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 13.728805) (2, 17.909194) (3, 23.324666) (4, 28.030819) (5, 33.279611) 
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 13.841305) (2, 12.801791) (3, 13.358389) (4, 13.200611) (5, 13.251902)
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          ]
          coordinates {
            (1, 81.546486) (2, 85.345444) (3, 90.532347) (4, 98.247764) (5, 105.423875) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 25.539097) (2, 24.432485) (3, 25.629666) (4, 23.935250) (5, 23.911139)
          };
      \end{axis}
    \end{tikzpicture}
    % graph \includegraphics[width=.4\linewidth]{image1}
    \caption{Depth benchmark with precompilation}%
    \label{fig:erase-precomp}
  \end{subfigure}
  \caption{The above results depict the behavior of both algorithms in depending on the \text{depth} of potential partial matches. The lines with square entry points represent problems where unification is easy. The lines with circle entry points are the same tests with hard unification problems.}%
  \label{fig:erase}
  \end{figure}

>>>>

  \keywords{Forward Reasoning \and Forward Chaining \and Tactics \and Interactive Theorem Proving}
\end{abstract}

@@

\begin{figure}
  Depth Test
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        %title={Depth Test},
        xlabel={Depth},
        ylabel={Time in ms},
        xmin=1, xmax=5,
        ymin=8, ymax=2^10,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 35.466292) (2, 40.918638) (3, 46.936125) (4, 54.933124) (5, 61.269861)
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 135.967736) (2, 127.324444) (3, 136.891250) (4, 118.720444) (5, 116.293222) 
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          ]
          coordinates {
            (1, 107.978069) (2, 115.900527) (3, 122.454958) (4, 137.732764) (5, 144.037681) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 619.932611) (2, 601.456805) (3, 600.926110) (4, 589.144389) (5, 595.091180) 
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Depth benchmark no-precompilation}%
    \label{fig:erase-noprecomp}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        %title={Depth Test},
        xlabel={Depth},
        %ylabel={Time in ms},
        xmin=1, xmax=5,
        ymin=8, ymax=1024,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        yticklabels={},
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 13.728805) (2, 17.909194) (3, 23.324666) (4, 28.030819) (5, 33.279611) 
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 13.841305) (2, 12.801791) (3, 13.358389) (4, 13.200611) (5, 13.251902)
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          ]
          coordinates {
            (1, 81.546486) (2, 85.345444) (3, 90.532347) (4, 98.247764) (5, 105.423875) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 25.539097) (2, 24.432485) (3, 25.629666) (4, 23.935250) (5, 23.911139)
          };
      \end{axis}
    \end{tikzpicture}
    % graph \includegraphics[width=.4\linewidth]{image1}
    \caption{Depth benchmark with precompilation}%
    \label{fig:erase-precomp}
  \end{subfigure}
  \caption{The above results depict the behavior of both algorithms in depending on the \text{depth} of potential partial matches. The lines with square entry points represent problems where unification is easy. The lines with circle entry points are the same tests with hard unification problems.}%
  \label{fig:erase}
  \end{figure}
